Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
Add class authors + pdf

author-information:
    - \author{Eric N. Smith*, Robert X. D. Hawkins*, the students of Psych 254, and Michael C. Frank}

@@

author-note:
    "These authors contributed equally. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."

>>>>

author-information:
    - \author{Eric N. Smith*, Robert X. D. Hawkins*, the students of Psych 254**, and Michael C. Frank}

@@

author-note:
    "*These authors contributed equally. **Project contributors included Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampien, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, Jed Tan. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."
